### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

>>>>

In the section, we discuss the limitations, usages, and some future work. 
%
\tool{} works on native x86 execution traces. The design, which is very
precise in terms of true leakages compared to other static source code
method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has 
the common limitations of dynamic approaches. \tool{} may only cover part of the code.
  % Each time we only get one single execution trace. Therefore,
We may 
neglect some side-channel vulnerabilities not covered by the traces analyzed.
However, this is not a crucial problem for analyzing crypto libraries because crypto
libraries are designed to have the same code coverage for various inputs. Our
evaluation also confirms the above point. For symmetric encryptions, during our
evaluation there is no secret-dependent control-flow transfers. RSA
implementations have several secret-dependent control-flow transfers. 
  %But after we manually check those leakages cites. We find
Most of them are  %used for
bound checks, which do not leak much information and have negligible effects
on the whole code coverage as well.
